Stage-Splitting a Modal Language

### 2014-07-31 paper/splitting.tex
changed theorems to support opens terms

We give the following end-to-end correctness lemmas for closed terms. 
Open term versions forthcoming.
The jury is still out on how to make these strong enough to prove that the partitioning between stages is correct.

\begin{lemma}
If $\cdot\vdash e : A \splittwosym [p,l.r]$ then,
\begin{itemize}
\item $\cdot \vdash e : A~@~\bbtwo$ 
\item $\diatwo [\cdot] e q$ iff $\reduce p u$ where
\item $q \equiv (\letin{l}{u}{r})$
\end{itemize}
\end{lemma}

\begin{lemma}
If $\cdot\vdash e : A \splitonesym [c,l.r]$ then,
\begin{itemize}
\item $\typesone [\cdot] e A$ 
\item $\diaone [\cdot] e {\xi;v}$ iff $\reduce c {(v_1,u)}$ where
\item $\dom \xi \vdash v \vsplito [v_1,v_2]$
\item $\reify \xi {v_2} q$
\item $q \equiv (\letin{l}{u}{r})$
\end{itemize}
\end{lemma}

>>>>

We give the following end-to-end correctness lemmas for open terms. 
It's a bit of a mess currently, but the $\Gamma$ is supposed to be all of the stage \bbone\ bindings, 
whereas $\Gamma'$ is the stage \bbtwo\ bindings.
Substitution splitting works just like value splitting, which is why they use the same symbol.

The jury is still out on how to make these strong enough to prove that the partitioning between stages is correct.

\begin{lemma}
If $\Gamma, \Gamma'\vdash e : A \splittwosym [p,l.r]$ then for all substitutions $\gamma : \Gamma$,
\begin{itemize}
\item $\Gamma,\Gamma' \vdash e : A~@~\bbtwo$ 
\item $\gamma \vsplito [\gamma_1, \gamma_2]$
\item $\diatwo [\Gamma'] {\gamma(e)} q$ iff $\reduce {\gamma_1(p)} u$ where
\item $\Gamma' \vdash q \equiv (\letin{l}{u}{\gamma_2(r)})$
\end{itemize}
\end{lemma}

\begin{lemma}
If $\Gamma, \Gamma'\vdash e : A \splitonesym [c,l.r]$ then for all $\gamma : \Gamma$,
\begin{itemize}
\item $\typesone [\Gamma, \Gamma'] e A$ 
\item $\gamma \vsplito [\gamma_1, \gamma_2]$
\item $\diaone [\Gamma'] {\gamma(e)} {\xi;v}$ iff $\reduce {\gamma_1(c)} {(v_1,u)}$ where
\item $\Gamma',\dom \xi \vdash v \vsplito [v_1,v_2]$
\item $\reify \xi {v_2} q$
\item $\Gamma'\vdash q \equiv (\letin{l}{u}{\gamma_2(r)})$
\end{itemize}
\end{lemma}
